---
title: "Assessing Student Satisfaction"
author: "Bagilidad, Olivo, Talon"
date: "2024-04-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

------------------------------------------------------------------------

# Assessing Student Satisfaction in Online Shopping

------------------------------------------------------------------------

#### Load CSV Data

```{r}
#install.packages("readr")
#install.packages("dplyr")
#install.packages("ggplot2")
#install.packages("tidyr")
#install.packages("stringr")
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)


student_satisfaction <- read.csv("student_satisfaction.csv")

str(student_satisfaction)
summary(student_satisfaction)
```

#### Remove Useless Rows

```{r}

student_satisfaction <- student_satisfaction %>%
  filter(prefered_platform != "None")

```

#### Question Columns

```{r}

question_columns <- c("U6", "RA1", "RA5", "OE7", "EOU3", "EOUS", "EOU6", "EU4", "A1", "AF1", "AF2", "Affect1", "SN1", "SN2", "SF2", "SF4", "PBC2", "PBC3", "PBC5", "FC3", "SE1", "SE4", "SE6", "SE7", "ANX1", "ANX2", "ANX3", "ANX4", "BI1", "BI2", "BI3")

```

#### Change Blank Cells to NA

```{r}

student_satisfaction <- student_satisfaction %>% 
  mutate_all(na_if, "")

```

#### Change Columns to a Factor

```{r}

# Change questions column to factor
for (column_name in question_columns) {
  student_satisfaction[[column_name]] <- factor(student_satisfaction[[column_name]],
                              levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
                              ordered = TRUE)
}

# Change preferred platform column to factor
student_satisfaction$prefered_platform <- factor(student_satisfaction$prefered_platform, 
                                     levels = c("Shopee", "Lazada", "TikTok", "Shein"))

# Change online_shopping_freq column to factor
student_satisfaction$online_shopping_freq <- factor(student_satisfaction$online_shopping_freq, 
                               levels = c("Rarely", "Occasionally", "Monthly", "Weekly", "Daily"))

```


#### Separate demographic, shopping behavior, and determinant columns

```{r}

demographic_cols <- c("Timestamp", "name", "age", "gender", "grade_level", "address", "contact", "prefered_platform", "online_shopping_freq")
demographics <- student_satisfaction %>% 
  select(all_of(demographic_cols))

determinant_cols <- setdiff(names(student_satisfaction), demographic_cols)
determinants <- student_satisfaction %>% 
  select(all_of(determinant_cols))


```

#### Category Map 

```{r}

category_map <- list(
  "Performance Expectancy" = c("U6", "RA1", "RA5", "OE7"),
  "Effort Expectancy" = c("EOU3", "EOUS", "EOU6", "EU4"),
  "Attitude toward using technology" = c("A1", "AF1", "AF2", "Affect1"),
  "Social influence" = c("SN1", "SN2", "SF2", "SF4"),
  "Facilitating Conditions" = c("PBC2", "PBC3", "PBC5", "FC3"),
  "Self-Efficacy" = c("SE1", "SE4", "SE6", "SE7"),
  "Anxiety" = c("ANX1", "ANX2", "ANX3", "ANX4"),
  "Behavioral Intention to Use the System" = c("BI1", "BI2", "BI3")
)
category_df <- stack(category_map)
colnames(category_df) <- c("question", "category")

```

#### Converting Determinants to numeric then mean and standard deviation and joining with category map

```{r}

determinants_means <- determinants %>%
  mutate(across(everything(), as.numeric)) %>%
  summarise_all(.funs = mean) %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "mean")

determinants_sds <- determinants %>%
  mutate(across(everything(), as.numeric)) %>%
  summarise_all(.funs = sd) %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "sd")


determinant_summary <- determinants_means %>%
  inner_join(determinants_sds, by = "question") %>%
  inner_join(category_df, by = "question")

determinant_summary

```

#### Get mean and sd by category

```{r}

determinant_mean_by_category <- aggregate(mean ~ category, determinant_summary, mean)
determinant_sd_by_category <- aggregate(sd ~ category, determinant_summary, sd)

determinant_summary_by_category <- determinant_mean_by_category %>%
  inner_join(determinant_sd_by_category, by= "category")

determinant_summary_by_category

#write.csv(determinant_summary_by_category, "determinant_mean_sd.csv")
```

#### Clean Demographics

```{r}
library(dplyr)
demographics <- demographics %>%
  select(-Timestamp, -name, -contact, -address)

demographics <- demographics %>%
  mutate_all(tolower)

# gender
demographics$gender[!(demographics$gender %in% c("male", "female"))] <- "other"

# age
demographics$age <- as.numeric(demographics$age) 
demographics <- demographics[!is.na(demographics$age) & demographics$age < 24, ] 
age_bins <- c(14, 18, 24)
labels <- c("14-18", "19-24")
demographics$age_group <- cut(demographics$age, breaks = age_bins, labels = labels, right = FALSE)


# grade level
demographics$grade_level <- gsub("senior", "", demographics$grade_level) 
demographics$grade_level <- str_trim(demographics$grade_level)


# convert to factor
demographics$gender <- as.factor(demographics$gender)
demographics$grade_level <- as.factor(demographics$grade_level)
demographics$prefered_platform <- as.factor(demographics$prefered_platform)
demographics$online_shopping_freq <- factor(demographics$online_shopping_freq, 
                           levels = c("rarely", "occasionally", "monthly", "weekly", "daily"), 
                           ordered = TRUE)


str(demographics)


#write.csv(demographics, "cleaned-demographics.csv")

```

### Visualization for determinants 
```{r}
determinant_mean_sd <- read_csv("determinant_mean_sd.csv")

determinant_plot <- ggplot(determinant_mean_sd,aes(x=category, y=mean))+
                    geom_bar(stat='identity', fill='beige')+
                    geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd),width=0.4,position=position_dodge(0.9))+
                    labs(title = "Mean with Standard Deviation",
                    x = "Category",
                    y = "Mean") +
                    theme(plot.title = element_text(hjust = 0.5),
                    axis.text.x = element_text(angle = 45, hjust = 1))
determinant_plot


```

### Visualization for Demographics
```{r}
cleaned_demographics <- read_csv("cleaned-demographics.csv")

#Online shopping frequency by age group
ageShoppingFreq_plot <- 
  ggplot(cleaned_demographics, aes(x = age, fill = online_shopping_freq)) +
  geom_bar(position = "fill") +
  labs(title = "Online Shopping Frequency by Age Group",
       x = "Age Group",
       y = "Proportion",
       fill = "Online Shopping Frequency")
ageShoppingFreq_plot



# Bar plot for online shopping frequency by age group
ageShoppingFreq_plot <- ggplot(cleaned_demographics, aes(x = age_group, fill = online_shopping_freq)) +
  geom_bar(position = "fill") +
  labs(title = "Online Shopping Frequency by Age Group",
       x = "Age Group",
       y = "Proportion",
       fill = "Online Shopping Frequency")

ageShoppingFreq_plot 

```